\section{Meeting: January 12th, 2018}


Problem, Anneke:
	- when we meet new people, can we trust this person
	- not really possible, go on cues, but we're really bad at picking trust cues 
	- define trust: is someone a good investment
		define good: they will invest back in us
	- it's great if you never leave your community
	- what if you move, then your trust is not portable


Joao:
	- a central body that approves prosocial people

	- a sink: that turn tokens into cash 
		- a subset of people that exchange cash into tokens

		ie: artists are sinks, they can turn token into currency. Currency come from pool high wealth individuals. Artists are validated by a central body. 

tzuo : why is the central body not the sink?
joao : you don't want anyone to just get money. 

tzuo : why not just use money, why use tokens?
joao: artists are the only ones that can convert to cash.
	artists are not miners. the path is of currency flow is pro-social in nature. there is another person that validates the transaction

timm: do you generate new coins in the process of validating the transaction.

joao: that's on the table. 

timm: why can't I buy off the validator?
joao: the validator can only validate a certain number of times. one person can't always be the auditor. Need a way to ensuring w/i every triangle in the graph, the triangle can only happen some number of times. 

anneke: limited transaction may be unrealistic.

timm: system of authentication w/ trust component. so if you know you do something prosocial, how do you authenticate yourself during that transaction. and show that you are trust-worthy. first idea is we have web of trust and chain of trust.

chain of trust: one single authority who certificates other people that are able to authenticate themselves. a tree like structure. 

web of trust: private-public key infrastructure. I know you and I will sign you as trustworthy. Somoene gets more trust worthy w/ number of your certificates. 

joao: more prosocial transaction means more trustworthy. Accumulation of tokens is not as good as number of transactions. 

anneke: it would be nice integrate a compoenent where you evaluate people you know really well. there's a lot of people that we know well but don't trust them.

tzuo: it's called "power of attorney". it's a power of attonery that's made public. 

define pro-social: any action that costs you but benefit others.

timm: we want to ensure cases such as (kill people) are outliers.

tzuo: blockchain used by UN to make accounting cheap and transparent for giving out stuff. They don't verify what is the items that are being exchanged. 













