\section{Meeting: January 12th, 2018}

Members: Xiao Ling, Joao Sedoc, Anneke Buffone, Tzuo Hann Law, Zack P

First 10 minutes, just summarizing what was said last time.


Joao: 

miner: teacher
sink : artists

1. teachers are rewarded, they have wallets and based on some rate, they generate tokens. And they give tokens to someone else when they do something prosocial. 

2. the person with the token can , ie buy artwork with tokens, and artist can take token and exchange it with the central lobby and get cash. 

Zack: are teachers an arbitrary choice?

Joao: yes, I'm just trying to make it concrete. 

anneke: charitable donation to an agency?

joao: that's the opposite of what we want, charitable donation to the pool would be what we want. This is better since as the token flows through the system, it is leveraged up for a series of pro social behavior. 

Zack: what about scraping twitter and measuring pro social behavior? Given the background makes sense. 

Tzou: 
1. Can we reward guys that give more reviews. 
2. What about open source code? can you be paid using tokens, it's easy to to verify usage,   what about ownership? 
3. What about reddit, accumulation of upvotes, is that something that's monentizable?
4. Papers, what if you get paid by the citation?
	- but I can't just vote on mine, 
	- maybe have a importance factor

5. In china, credit history is tied to online presence, then you can spend that number. 

going along the sink-miner framework, ask for an endowment, then we make 10 dollar per second. we let the teachers mine the tokens, and then take the token and go immediable to the sink, there's some discount factor, ie 1/100th at origination. You want to pass this token as many times as you can through the chain. You must not be able to figure whic token is at maturity. Verification is such that if you don't particiapte after some time, then it dissappear. This bypass druglord that buys everything from teacher and convert, he has to pass through the system, then only way to mature the token is to pass through the system, and go through as many verification. 

the point is: the value of my wallet is monotocially increasing, but you don't know how much by each transaction. The value is a function of maturity, maturity is a function of number of transactions. 


Tzuo: we should muddle through one problem. So my friends can help us poke through the problems. 


Zack: online ideas for prosocial network.

- github
- reviews
- twitter interactions:

prosocial version of online communities. That's as concrete as I've gotten. I like the.

Tzuo: let's pick one vertical and start a specific solution

Zack: how do you combine the different communites. If we solve one specific problem, how do you generalize to other markets? 

Tzuo: maybe trying to measure "good" in real life is not a problem we should attempt. Real life is the combination of many micro communities. So we just have figure out how to reward behavior in each platform, where protocl against spam and bots. then we have to figure out how to figure how what the exchange rate is between them. 

Joao: we can start with ie Airbnb and help new people to be verified. 

Tzuo: can we have a way to figure out if someone is trustworthy w/o revealing identities. 
suppose there's not bot rising, each community would give us the measure of "trust". 

Joao: let's start w/ something easier, in theory feasible. 

Zack: as for token worth, we can have different upvotes be worth various amounts. 

Tzuo: if I was nice one platform, I would like to start on the other platform. 

Zack: if you're a startup, you want the first 1000 users to be full of people that are token holders. Because you get a better user experience. 

Joao: it helps AirBnB because most people are coming into your apartment are risky, if they havn't done too many AirBnB, then it's harder to verify. actually verifying who these people are is difficult, ie scan passport. AirBnB has tried to make incentives for reviewers and people who review, they need this service. And their community is limited. And it really helps people are AirBnB competitors. 

Decision: we are in agreement to lean on online committee.

Tzuo: one protocol. Warren Buffet gives us money. the only way to exchange tokens for money is with Joao. Joao's wants people who's nice in their community, and judge in other communities. There's no trading, only person you can trade is with Joao. If I want to be rich, I want a lot of tokens => do good stuff in reddit, airbnb, etc. I also have to do something for the community, your networth will fluctuate based on how your voting of other community lines up with population average. This way we can illicit this person's behavior so that he's honest, and votes in a way that's good system. If everyone thinks your coummnity is great, then your networth goes up.  

Joao: how do you mine

Tzuo: by participating in the community, everyone is a miner. 

Zack: how do you measure prosocial behavior

Tzuo: not sure we have to work it out. How do you elicit votes on other community. Ie, everday you're given a choice of which token from another community. the more you want it, the more it's worth to you. Suppose I'm the top dude in the Bernie, then if I want Bernie's tokens, then I'll increase the value of my own tokens ... 

Action items: 

1. Tzuo will write down his thoughts in more cogent manner
2. Joao: lawer, can think of three people ... who I could ask
3. Zack: I also have some people to ask. 
4. Zack: look into reddit API:
	- Reddit
	- Stackoverflow
	- Wikipedia
	- Quora


